Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-09-06 Paper/method.tex
..

The above comparisons establish consistency between gradient-based and
gradient-free approaches. This indicates that the local linear approximation
of the model output resulted in a reasonably accurate estimation of the
gradients in this case. In the following section, we shift our focus to 
the high-dimensional H$_2$/O$_2$ reaction kinetics application involving
33 uncertain inputs.

>>>>

The above comparisons indicate that the two strategies yield consistent results for the 19-dimensional
H$_2$/O$_2$ reaction kinetics problem. In other words, the gradient estimates using pertubation and
regression are reasonably close, and therefore, using the regression-based strategy would be computationally
advantageous in this case. In the following section, we shift our focus to 
the higher-dimensional H$_2$/O$_2$ reaction kinetics application involving 33 uncertain inputs.
